\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\onehalfspacing

\begin{document}

\begin{center}
{\Large\bfseries Title Page}
\end{center}

\bigskip

\noindent\textbf{Title:} Analytical uncertainty of the statistical paradigm as a stochastic risk vector in soil quality assessment under long-term conservation management

\bigskip

\noindent\textbf{Authors:}

\medskip

\noindent
Luiz Diego Vidal Santos\textsuperscript{2,*},
Alceu Pedrotti\textsuperscript{1},
Jusimara de Andrade Santos\textsuperscript{1},
Jaelson Souza Ara\'{u}jo\textsuperscript{4},
Sara Julliane de Ara\'{u}jo Santos\textsuperscript{1},
Emersson Guedes da Silva\textsuperscript{4},
Renisson Neponuceno de Ara\'{u}jo Filho\textsuperscript{3},
Brisa Marina da Silva Andrade\textsuperscript{1},
J\'{e}mison Mattos dos Santos\textsuperscript{5},
Francisco Sandro Rodrigues Holanda\textsuperscript{4}

\bigskip

\noindent\textbf{Affiliations:}

\medskip

\noindent
\textsuperscript{1} PRODEMA, Universidade Federal de Sergipe, S\~{a}o Crist\'{o}v\~{a}o, Sergipe, Brazil\\[3pt]
\textsuperscript{2} DCHF, Universidade Estadual de Feira de Santana, Feira de Santana, Bahia, Brazil\\[3pt]
\textsuperscript{3} DTR, Universidade Federal Rural de Pernambuco, Recife, Pernambuco, Brazil\\[3pt]
\textsuperscript{4} DEA, Universidade Federal de Sergipe, S\~{a}o Crist\'{o}v\~{a}o, Sergipe, Brazil\\[3pt]
\textsuperscript{5} Universidade Estadual de Santa Cruz, Ilh\'{e}us, Bahia, Brazil

\bigskip

\noindent\textbf{*Corresponding author:}\\
Luiz Diego Vidal Santos\\
DCHF, Universidade Estadual de Feira de Santana\\
Av. Transnordestina, s/n, Novo Horizonte\\
CEP 44036-900, Feira de Santana, Bahia, Brazil\\
E-mail: ldvsantos@uefs.br

\bigskip

\noindent\textbf{ORCID:}

\medskip

\noindent
Alceu Pedrotti: \\
Luiz Diego Vidal Santos: 0000-0001-8659-8557\\
Jusimara de Andrade Santos: \\
Jaelson Souza Ara\'{u}jo: \\
Sara Julliane de Ara\'{u}jo Santos: \\
Emersson Guedes da Silva: 0009-0004-9742-6215\\
Renisson Neponuceno de Ara\'{u}jo Filho: \\
Brisa Marina da Silva Andrade: \\
Francisco Sandro Rodrigues Holanda: 0009-0000-9358-0531

\bigskip

\noindent\textbf{Declarations:}

\medskip

\noindent\textbf{Funding:} This study was financed in part by the Coordena\c{c}\~{a}o de Aperfei\c{c}oamento de Pessoal de N\'{i}vel Superior -- Brazil (CAPES) and by the Conselho Nacional de Desenvolvimento Cient\'{i}fico e Tecnol\'{o}gico (CNPq).

\medskip

\noindent\textbf{Conflict of interest:} The authors declare no competing interests.

\medskip

\noindent\textbf{Ethics approval:} Not applicable.

\medskip

\noindent\textbf{Consent to participate:} Not applicable.

\medskip

\noindent\textbf{Consent for publication:} Not applicable.

\medskip

\noindent\textbf{Data availability:} The anonymized dataset and all analysis routines (R and Python) used in this study are available at \url{https://doi.org/10.5281/zenodo.19390736}.

\medskip

\noindent\textbf{Author contributions:}\\
\textbf{A. Pedrotti}: Supervision, Project administration, Resources, Investigation, Funding acquisition.
\textbf{L.D.V. Santos}: Conceptualization, Methodology, Software, Formal analysis, Visualization, Writing -- original draft.
\textbf{J.A. Santos}: Investigation, Data curation.
\textbf{J.S. Ara\'{u}jo}: Investigation, Data curation.
\textbf{S.J.A. Santos}: Investigation, Data curation.
\textbf{E.G. Silva}: Investigation, Data curation.
\textbf{R.N. Ara\'{u}jo Filho}: Methodology, Validation, Writing -- review \& editing.
\textbf{B.M.S. Andrade}: Investigation, Data curation.
\textbf{F.S.R. Holanda}: Supervision, Resources, Funding acquisition.
All authors read and approved the final manuscript.

\end{document}
